The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
conclusion edits

## Habitat selection and space use
<!-- TODO: Gerard ‘openness’ paper -->
Social structure is influenced by resource availability and seasonality
[@Peignier_2019], configuration [@He_2019] and fragmentation [@Banks_2007].
Habitat selection, the disproportionate use of available resources or landscape
features by animals [@Manly_1993; @Boyce_1999], is a scale dependent process
[@Mayor_2009]. Combined, social structure and habitat selection are intimately
linked as individuals must share space to interact and the distribution of
resources influences group dynamics and home range size [@Webber_2018].
<!--Animals select habitats at multiple scales ... (Mayor)  Mayor scale -->
Multilayer networks represent a novel framework for considering the influence of
habitat selection and space use on sociality across scales.

@@

<!-- TODO: point to figure 1 -->
Habitat selection depends on the scale at which it is measured and a singular
scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
selection is measured using resource selection functions (RSFs), based on the
proportion of used and available resources for an animal [@Manly_1993;
@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
the geographical range of a species, (2) the home range of an individual, (3)
the habitat patches within the home range and (4) specific resources within a
habitat patch. Moving past this hierarchical perspective, Mayor (2009)
reviewed types of scale relevant in measurement of habitat selection and recommend using a continuum of scales for identifying characteristic scales of selection. For example, @Mayor_2007 showed caribou selection for shallow snow across all sales and used to a continuum of scales to avoid bias from narrowing the measurements to scales assumed to be associated with certain behaviours.

@@

Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology. We demonstrate novel analyses that vary social, spatial, and temporal
scale within a multilayer framework. In our caribou case study, we show that (1)
multilayer social networks can be, but are not always, scale dependent, and (2)
the use of multilayer networks could be useful for identifying habitat or
season-specific social processes. Our analyses of social, spatial, and temporal
scales in multilayer network framework highlight potential to identify scales at
which different properties of layers within a multilayer network show the most
variability. Furthermore, we discuss the potential integration of individual
phenotypes and fitness, collective movement, and habitat selection for future
analyses considering spatial ecology using multilayer networks.

@@

Multilayer networks are complicated in that they can incorporate data as varied
as social interactions, landscape features, and seasons, all of which exist at
different scales and units of measurement. Our analysis of caribou multilayer
networks incorporated high resolution GPS telemetry data and spatial landcover
data is grounded in the context of observed animal social networks, as the
scales we chose to explore (e.g., number of observations, sociality across space
and time) are ones that can be observed as has traditionally been done. Thus, we
highlight ways in which scale ought to be considered for both observed and
remotely-sensed data when building social networks. Furthermore, GPS telemetry
data provides a link between large scale landscape properties and fine scale
social interactions as animal movement occurs across the landscape, and when
taken into account with multiple individuals can indicate association patterns.
Thus, a layer incorporating relocation data could be a great boon linking
spatial and social layer in multilayer networks.
<!-- JWT: I'm having a hard time getting to where I want to go, but basically I want to highlight that using GPS relocation data is reflective of more traditional observed networks like they wanted when they accepted our abstract, and this provides opportunities for social networks, particularly multilayer networks. It may be easier to scale relocation data and other landscape variables and can link to smaller scale observed interactions, providing a bridge between different types of data. -->

@@

1. How do social phenotypes vary across social, temporal, and spatial scales and
differentially influence fitness? Are some scales better predictors for
different fitness metrics?
2. Why do individuals associate more strongly with certain conspecifics in some
habitats? What, if any, is the role of movement in the context of habitat
networks?
3. How, and why, does the spatial scale of perception influence, e.g. auditory,
visual, or chemotaxis, influence the  social environment? What is the role of
memory, and by extension social and spatial cognition, as animals navigate their
environment and make decisions about where to move next?

>>>>

## Habitat selection and space use
<!-- TODO: Gerard ‘openness’ paper -->
Social structure is influenced by resource availability and seasonality
[@Peignier_2019], configuration [@He_2019] and fragmentation [@Banks_2007].
Habitat selection, the disproportionate use of available resources or landscape
features by animals [@Manly_1993; @Boyce_1999], is a scale-dependent process
[@Mayor_2009]. Combined, social structure and habitat selection are intimately
linked as individuals must share space to interact and the distribution of
resources influences group dynamics and home range size [@Webber_2018].
<!--Animals select habitats at multiple scales ... (Mayor)  Mayor scale -->
Multilayer networks represent a novel framework for considering the influence of
habitat selection and space use on sociality across scales.

@@

<!-- TODO: point to figure 1 -->
Habitat selection depends on the scale at which it is measured and a singular
scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
selection is measured using resource selection functions (RSFs), based on the
proportion of used and available resources for an animal [@Manly_1993;
@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
the geographical range of a species, (2) the home range of an individual, (3)
the habitat patches within the home range and (4) specific resources within a
habitat patch. Moving past this hierarchical perspective, Mayor (2009)
reviewed types of scale relevant in measurement of habitat selection and recommend using a continuum of scales for identifying characteristic scales of selection. For example, @Mayor_2007 showed caribou selection for shallow snow across all sales and used to a continuum of scales to avoid bias from narrowing the measurements to scales assumed to be associated with certain behaviors.

@@

Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology. We demonstrate the potential novel analyses that vary social, spatial, and temporal
scale within a multilayer framework. In our caribou case study, we show that (1)
multilayer social networks can be, but are not always, scale-dependent, and (2)
the use of multilayer networks could be useful for identifying habitat or
season-specific social processes. Our analyses of social, spatial, and temporal
scales in multilayer network framework highlight potential to identify scales at
which different properties of layers within a multilayer network show the most
variability. Furthermore, we discuss the potential integration of individual
phenotypes and fitness, collective movement, and habitat selection for future
analyses considering spatial ecology using multilayer networks.

@@

Multilayer networks are complicated in that they can incorporate data as varied
as social interactions, landscape features, and seasons, all of which exist at
different scales and units of measurement. Our analysis of caribou multilayer
networks incorporated high resolution GPS telemetry data and spatial landcover
data is grounded in the context of observed animal social networks, as the
scales we chose to explore, e.g., number of observations, sociality across space
and time, are ones that can be observed as has traditionally been done in ethology. Thus, we
highlight ways in which scale ought to be considered for both observed and
remotely-sensed data when building social networks. Furthermore, GPS telemetry
data provides a link between large scale landscape properties and fine scale
social interactions as animal movement occurs across the landscape, and when
taken into account with multiple individuals can indicate association patterns.
Thus, a layer incorporating relocation data could be a great boon linking
spatial and social layer in multilayer networks.
<!-- JWT: I'm having a hard time getting to where I want to go, but basically I want to highlight that using GPS relocation data is reflective of more traditional observed networks like they wanted when they accepted our abstract, and this provides opportunities for social networks, particularly multilayer networks. It may be easier to scale relocation data and other landscape variables and can link to smaller scale observed interactions, providing a bridge between different types of data. -->

@@

1. How do social phenotypes vary across social, temporal, and spatial scales and
at which scale might these influence fitness? Are some scales better predictors for
different fitness metrics?
2. Why do individuals associate more strongly with certain conspecifics in some
habitats? What, if any, is the role of movement in the context of habitat
networks?
3. How, and why, does the spatial scale of perception influence, e.g. auditory,
visual, or chemotaxis, influence the  social environment? What is the role of
memory, and by extension social and spatial cognition, as animals navigate their
environment and make decisions about where to move next?
